Deployable Probabilistic Programming

### 2019-04-17 paper/paper.tex
hello world example, more references

\lstset{ % add your own preferences
    frame=none,
    basicstyle=\ttfamily\footnotesize,
    numbers=none,
    numbersep=5pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

@@

The \lstinline{Observe} method computes the log-likelihood of
the distribution parameters. The Normal distribution has two
parameters: mean $\mu$ and standard deviation
$\sigma$. To ease the inference, positive $\sigma$ is transformed to
unrestricted $\log \sigma$, and the parameter vector is $[\mu,
\log \sigma]$. \lstinline{Observe} first imposes a prior on the
parameters, and then conditions the posterior distribution on
the observations:

@@

Inference:

@@

// Parameters
mean, logs := 0, 0
x := []float64{mean, logs}
\end{lstlisting}

Optimization:

\begin{lstlisting}
opt := &infer.Momentum{
    Rate:  0.01,
    Decay: 0.998,
}
for iter := 0; iter != 1000; iter++ {
    opt.Step(m, x)
}
mean, logs = x[0], x[1]
\end{lstlisting}

Posterior:

@@

@@

\section{Case Studies}

>>>>

\lstset{ % add your own preferences
    frame=single,
    basicstyle=\ttfamily\footnotesize,
    numbers=none,
    numbersep=5pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

@@

The \lstinline{Observe} method computes the log-likelihood of
the distribution parameters. The Normal distribution has two
parameters: mean $\mu$ and standard deviation
$\sigma$. To ease the inference, positive $\sigma$ is transformed to
unrestricted $\log \sigma$, and the parameter vector \lstinline{x} is $[\mu,
\log \sigma]$. \lstinline{Observe} first imposes a prior on the
parameters, and then conditions the posterior distribution on
the observations:

@@

For inference, we supply the data and optionally initialize the
parameter vector. Here the data is hard-coded, but in general
can be read from a file, a database, a network connection,
or dynamically generated by another part of the program:

@@

// Parameters
x := []float64{}
\end{lstlisting}

The fastest and most straightforward inference is the maximum
\textit{a posteriori} (MAP) estimation, which can be done using
a gradient descent algorithm (Adam~\cite{KB15} in this case).

\begin{lstlisting}
opt := &infer.Adam{
    Rate:  0.01,
}
for iter := 0; iter != 1000; iter++ {
    opt.Step(m, x)
}
\end{lstlisting}

To recover the full posterior distribution of
the parameters we use Hamiltonian Monte Carlo~\cite{N12}:

@@

Models are of course not restricted to linear code, and may
comprise multiple methods, contain loops, conditional
statements, function and method calls, and recursion. Case
studies~(Section~\ref{sec:case-studies}) provide elaborated
model examples.

@@

\section{Case Studies}
\label{sec:case-studies}
